\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgement}
It is with great honor I now present the product of two amazing years as a Master student. This thesis could not have been completed without considerable help from various people around me. Special thanks goes to my supervisors Trude Storelvmo and Morten Køltzow. For their supervision and helpful guidance, and not least their constructive criticism of my writing style. I would be remiss not to thank Johanne Mehren for tipping me off to the opportunity of this project, and of course for her friendship and jokes (Even or maybe especially those on my behalf).

I am of course indebted to Martin Boie Christiansen and Glenn Christiansen for their help and interest in this project. Their insights into the world of helicopters have been essential. I still am awaiting their offer to let me fly in one of their helicopters. 

The thesis was also written in a time of great global turmoil, as the world was hit by the COVID-19 pandemic. This in turn leads me to thank the Rian Julsrud family for their hospitality in letting me isolate from the rest of the world in their cellar. It is not an understatement that I have learned and continue to learn immensely by our talks at the coffee- and dinner tables.

The list of people who I owe thanks to contains a myriad of names. I would love to list them all but, the paper usage would not be defensible. Instead I would thank a special few who is not aforementioned: My mother and father, my American proofreader and friend Jonah Shaw, my brothers Tobias and Alphonse, and the Ingeborg(s) \\

\begin{center}
\textbf{Johannes Tobiassen Langvatn}
\end{center}
\begin{center}
\textbf{July 2020}
\end{center}
\includecomment{, and last but never least, my friend Leila who passed during the work of this thesis.}

\includecomment{
-Acknowledge Martin Boie Christiansen
-Avinor
-Morten and Trude
-The jussruds
}